FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-20 NewVersion/paper.tex
small fix. to 25pages

\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
\newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
\newcommand\marco[1]{\authornote{marco}{blue}{#1}}
\newcommand\marcoT[1]{\authorText{blue}{#1}}
\newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}

%\newcommand\bruno[1]{}
%\newcommand\yanlin[1]{}
%\newcommand\marco[1]{}
%\newcommand\haoyuan[1]{}

@@

% \authorinfo{NoAuthor}
%            {The University of Hong Kong, China}
% %           {\{ylwang,hyzhang,bruno\}@cs.hku.hk}
% %\authorinfo{Marco Servetto}
% %          {Victoria University of Wellington, New Zealand}
% %          {marco.servetto@ecs.vuw.ac.nz}
\author{Yanlin Wang\inst{1} \and Haoyuan Zhang\inst{1} \and Bruno C.d.S. Oliveira\inst{1} \and Marco Servetto\inst{2}}
\institute{The University of Hong Kong \and Victoria University of Wellington \\ \email{ylwang@cs.hku.hk, hyzhang@cs.hku.hk, bruno@cs.hku.hk, marco.servetto@ecs.vuw.ac.nz}}

@@

\bibliographystyle{splncs03}
\bibliography{paper}

>>>>

% \newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
% \newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
% \newcommand\marco[1]{\authornote{marco}{blue}{#1}}
% \newcommand\marcoT[1]{\authorText{blue}{#1}}
% \newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}

\newcommand\bruno[1]{}
\newcommand\yanlin[1]{}
\newcommand\marco[1]{}
\newcommand\haoyuan[1]{}

@@

% \authorinfo{NoAuthor}
%            {The University of Hong Kong, China}
% %           {\{ylwang,hyzhang,bruno\}@cs.hku.hk}
% %\authorinfo{Marco Servetto}
% %          {Victoria University of Wellington, New Zealand}
% %          {marco.servetto@ecs.vuw.ac.nz}
\author{Yanlin Wang\inst{1} \and Haoyuan Zhang\inst{1} \and Bruno C.d.S. Oliveira\inst{1} \and Marco Servetto\inst{2}}
\institute{The University of Hong Kong \and Victoria University of Wellington \\ \email{\{ylwang,hyzhang,bruno\}@cs.hku.hk, marco.servetto@ecs.vuw.ac.nz}}

@@

\newpage
\bibliographystyle{splncs03}
\bibliography{paper}
